Almost orthogonal vectors

### 2014-11-26 project3/paper/paper.tex
Added new figures
added an intro

\title{Almost Orthogonal vectors}

@@

\section{Introduction}
Given a dimension $n$ and a number $N > n$ of vectors, we want to find vectors $v_1, v_2, \ldots, v_N \in \mathbb{R}^n$ of unit length, such that
$$\epsilon = \max_{i \neq j} \{ |v_i \cdot v_j|^2 \}$$
is as small as possible.

>>>>

\title{Almost orthogonal vectors}

@@

\section{Introduction}
Consider a collection of $N$ unit vectors $v_1, \ldots, v_N$ in $\mathbb R^n$. Define $\epsilon$ as
\[\epsilon=\max_{i\neq j}|v_i\cdot v_j|^2.\]
For various $n$ and $N$, how do we minimize $\epsilon$?

For $n=N$, it is clear that the minimum value of $\epsilon$ is zero, obtained by letting $v_1,\ldots, v_N$ be any orthonormal basis. For fixed $n$, it is also easy to see that the minimum value of $\epsilon$ is nondecreasing as $N$ increases: that is, if $\epsilon_1$ is the minimum value of $\epsilon$ for $N$ unit vectors in $\mathbb R^n$, and $\epsilon_2$ is the minimum value of $\epsilon$ for $N+1$ unit vectors in $\mathbb R^n$, we must have $\epsilon_1\leq \epsilon_2$. Otherwise, given a configuration of $N+1$ vectors in $\mathbb R^n$ with $\epsilon=\epsilon_2$, we could simply remove one vector and obtain a configuration of $N$ vectors whose $\epsilon$ would be less than or equal to $\epsilon_1$.

Furthermore, given a configuration of $N$ vectors in $n$-space with corresponding $\epsilon$, we can obtain a collection of $N+1$ vectors in $\mathbb R^{n+1}$ with the same $\epsilon$: simply embed the first $N$ vectors in $\mathbb R^{n+1}$, then add any vector perpendicular to the hyperplane in which the $N$ vectors lie. Hence the minimum $\epsilon$ for collections of $N+1$ vectors in $\mathbb R^{n+1}$ is upper-bounded by the corresponding $\epsilon$ for $N$ vectors in $\mathbb R^n$.

In this paper, we shall see that, for $n=2$, the minimum value of $\epsilon$ will be given by 
\[\epsilon=\cos^2\pi/N.\] 
We shall also see that, for $N=n+1$, the minimum value of $\epsilon$ will be 
\[\epsilon=\frac{1}{n^2},\] 
with the $n+1$ vectors pointing to the vertices of the $n$-simplex.
